---
output: pdf_document
---

#Statistical Inference Course Project

Composed by: Akihiro Hayashi (21/03/2015)

#Summary

We reject that type of supplement doesn't affect tooth growth. And we also reject that dose deosn't affect tooth growth.

Outline of this project:

1. Summarize Dataset
2. Exploratory Data Analysis
3. Assumption
4. Test

##Summarize Dataset

```{r}
data(ToothGrowth)
head(ToothGrowth)
str(ToothGrowth)
summary(ToothGrowth)
library(dplyr)
df <- as.data.frame(group_by(ToothGrowth, supp, dose))
VC <- df[1:30, c(1, 3)]
OJ <- df[31:60, c(1, 3)]
```

##Exploratory Data Analysis

```{r}
par(mfrow = c(1, 2))
boxplot(len ~ dose, data = VC, xlab = "Dose", ylab = "Len", main = "VC")
boxplot(len ~ dose, data = OJ, xlab = "Dose", ylab = "Len", main = "OJ")
```

##Assumption

Paired Sample: From the description of this dataset, we know it's a paired sample with different means and variances when they are grouped by supp or dose.

##Test

We use test to do our analysis (not confidence interval).

###by Supp (H0: Supplement type doesn't affect tooth growth)

Rejection Rule: If supplement type doesn't affect tooth growth, p-value will be lower than significant level (.05).

```{r}
pv <- round(t.test(len ~ supp, data = ToothGrowth, paired = TRUE, var.equal = FALSE)$p.value, 3)
```

Our p-value is `r pv` (lower than 0.05), so we reject H0. Supplement type will affect tooth growth.

###by Dose (H0: Dose doesn't affect tooth growth)

We have to control supp variable. And as requirement, we cannot use ANOVA or regression, so we have to compare them 2 by 2.

```{r}
vc0510 <- round(t.test(len ~ dose, data = VC[1:20, ], paired = TRUE, var.equal = FALSE)$p.value, 4)
vc0520 <- round(t.test(len ~ dose, data = VC[-(11:20), ], paired = TRUE, var.equal = FALSE)$p.value, 4)
vc1020 <- round(t.test(len ~ dose, data = VC[11:30, ], paired = TRUE, var.equal = FALSE)$p.value, 4)
oj0510 <- round(t.test(len ~ dose, data = OJ[1:20, ], paired = TRUE, var.equal = FALSE)$p.value, 4)
oj0520 <- round(t.test(len ~ dose, data = OJ[-(11:20), ], paired = TRUE, var.equal = FALSE)$p.value, 4)
oj1020 <- round(t.test(len ~ dose, data = OJ[11:30, ], paired = TRUE, var.equal = FALSE)$p.value, 4)
p.value <- cbind(vc0510, vc0520, vc1020, oj0510, oj0520, oj1020)
colnames(p.value) = c("VC0510", "VC0520", "VC1020", "OJ0510", "OJ0520", "OJ1020")
test <- (p.value < 0.05)
rownames(test) <- "Result"
test
```

After doing t-test for each group, we can ALMOST reject H0, that is, dose will affect tooth growth. BUT, when comparing difference of tooth growth between 1 dose and 2 doses in OJ group, we failed to reject H0. So we might say, if we feed pigs orange juice, 1 or 2 doses may have little effect on tooth growth.

But, we may commit type I error when we seperate F-test into many t-tests. It will be better if we use ANOVA or regression to do it.